---
title: "Developing Data Product Week 4 Project"
author: "Dheeraj Singh"
date: "June 12, 2018"
output:
  beamer_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Purpose of Project

Developing Shiny App

- Use Shiny to build data product application and deploy it on Rstudio's servers
- Shiny Application should include some form of input (widget: textbox, checkbox, ...)
- Some operation on the ui input in sever.R
- Some reactive output displayed as a result of server calculationsll as the output of any embedded R code chunks within the document.

## R Presenter

- use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation for application
- It must be 5 pages
- Being hosted on github or Rpubs
- contained some embedded R code

## Shiny Application

- Application tries to explain different distribution models
- it explains Unifrom, uniform, Exponential and Cauchy distributions.
- Dynamic plots of the above distribution
- Used radio buttons to navigate in the app

## summary of the numbers

```{r, echo = TRUE,}

summary(runif(1:10000))
summary( rnorm(1:10000))
summary(rexp(1:10000))
summary(rcauchy(1:10000))

```

## Slide with Plot

```{r pressure}
par(mfrow = c(2,2))
hist(runif(1:10000), col = "gray")
hist(rnorm(1:10000), col = "gray")
hist(rexp(1:10000), col = "gray")
hist(rcauchy(1:10000), col = "gray")

```

